\section*{List of Author's Publications}

\subsection*{Home Conferences}

\noindent \textit{AFD001} \textbf{Foundations for homography estimation in presence of redundant point correspondencies} / \textbf{Milan Ondrašovič}, \textbf{Peter Tarábek}.

\noindent In: \textbf{Mathematics in science and technologies}: proceedings of the MIST conference 2020: proceedings of the MIST conference 2020 / Katarína Bachratá, Katarína Jasenčáková and Monika Smiešková. - 1. vyd. - [S.l.] : [s.n.], 2020. - 70 s. [print]. - ISBN 9798648566026. - s. 52-57 [print].

\noindent [Ondrašovič Milan ($50\%$) - Tarábek Peter ($50\%$)]

\noindent\rule{\textwidth}{0.4pt}

\noindent \textit{AFD002} \textbf{Object position estimation from a single moving camera} /\textbf{ Milan Ondrašovič}, \textbf{Peter Tarábek}, \textbf{Ondrej Šuch}.

\noindent In: \textbf{Information and digital technologies 2021}: proceedings of the international conference: proceedings of the international conference / [bez zostavovateľa]. - 1. vyd. - Danvers : Institute of Electrical and Electronics Engineers, 2021. - 370 s. - ISBN 978-1-6654-3692-2. - s. 31-37.
Zaradené v: SCOPUS

\noindent [Ondrašovič Milan ($50\%$) - Tarábek Peter ($40\%$) - Šuch Ondrej ($10\%$)]

\subsection*{International Journals}

\noindent \textit{ADC001} \textbf{Homography ranking based on multiple groups of point correspondences} / \textbf{Milan Ondrašovič} and \textbf{Peter Tarábek}.

\noindent In: \textbf{Sensors}. - Bazilej: Multidisciplinary Digital Publishing Institute. - [online, print]. - ISSN 1424-3210. - Roč. 21, č. 17 (2021), s. [1-17] [online, print].
Zaradené v: Current Content Connect ; SCOPUS ; Web of Science Core Collection

\noindent [Ondrašovič Milan ($50\%$) - Tarábek Peter ($50\%$)]

\noindent\rule{\textwidth}{0.4pt}

\noindent \textit{ADC002} \textbf{Siamese visual object tracking: a survey} / \textbf{Milan Ondrašovič} and \textbf{Peter Tarábek}.

\noindent In: \textbf{IEEE Access} : practical innovations, open solutions: practical innovations, open solutions. - Piscataway: Institute of Electrical and Electronics Engineers. - [online]. - ISSN 2169-3536 (online). - Roč. 9 (2021), s. 110149-110172 [online].
Zaradené v: Current Content Connect ; SCOPUS ; Web of Science Core Collection

\noindent [Ondrašovič Milan ($50\%$) - Tarábek Peter ($50\%$)]
