\thispagestyle{plain}

\begin{center}
    \Large{\textbf{Abstract}}
\end{center}

\noindent Visual object tracking is a challenging problem of current research and a central topic of this work. In this thesis, we disseminate our results concerning research in this area using deep machine learning tools. However, taking advantage of deep machine learning requires a large amount of data for model training and testing. With this in mind, we provide a short discussion of available and used datasets. More importantly, we provide a review of various approaches to tracking. As a result, object occlusion, one of the primary difficulties in object tracking, was selected as the problem to focus on. Besides tracking, this treatise includes similarity learning, a relevant and related area that is commonly approached using so-called Siamese neural networks. Consequently, the application of methods based on the aforementioned domain is not only discussed but also experimented with. Re-identification was explored to tackle object re-appearance after full occlusion. At the same time, to address the ramifications of the partial occlusion, we developed an attention-based approach. Latent spaces and embedding vectors were exploited to enhance the object ID propagation between frames. Moreover, one of the chapters is dedicated to our attempt to aid the tracking process using homography transformations. Throughout this dissertation, traffic analysis is frequently mentioned as the target real-world use case. Despite this specificity, the developed solutions and conclusions drawn from them apply to general object tracking with no specific constraints, although there is potential for additional improvement under concrete circumstances. Overall, few of the documented solutions did not yield the expected outcome. But, there are two contributions presented as two journal publications, namely an up-to-date comprehensive survey of Siamese-based tracking and the development of a new homography ranking method. The already promising results of the attention-based solution are still under proper validation and further evaluation.

\noindent \textbf{Keywords}: visual object tracking, deep machine learning, Siamese neural networks, latent spaces, attention mechanism, traffic analysis
